A Topic Model of Climate Change Literature

### 2017-05-02 main.tex

The topic model presented here is a rough map of climate change research since 1985. It shows the topics that make up this research and how they relate to each other, and demonstrates how this has changed over time.

>>>>

The topic model presented here is a rough map of climate change research since 1985. It shows a broad outline of the topics that make up this research and how they relate to each other, and demonstrates how this has changed over time. This relief map does not replace the maps drawn by assessment-makers-as-cartographers for policymakers described in \citet{Edenhofer2015}. Rather, it supplements it by reducing the exploration time necessary and acting as a reference, to compare how the assessment reflects the literature. [Rather, it provides a vital anchor.]

While topic modelling has been employed to answer specific questions about small aspects of climate literature, e.g. \citep[e.g.][]{minx2016negative,Sleeman2016}, this is the first application of topic models to gain an overview of the entire field.
